---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# singleRcaptureExtra

<!-- badges: start -->
[![R-CMD-check](https://github.com/ncn-foreigners/singleRcaptureExtra/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ncn-foreigners/singleRcaptureExtra/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/ncn-foreigners/singleRcaptureExtra/branch/main/graph/badge.svg)](https://app.codecov.io/gh/ncn-foreigners/singleRcaptureExtra/tree/main)
<!-- badges: end -->

An expention of `singleRcapture` package to handle fitted object from other R 
packages with zero truncated regression capabilities (and in the future the same
for ratio regression models)

### Quick demo

Utilizing additive models when effect is non linear:

```{r VGAM}
library(VGAM)
library(singleRcaptureExtra)
set.seed(123)
x <- rnorm(n = 1000)
y <- rpois(n = 1000, lambda = exp(-1 + cos(x)))
data <- data.frame(y = y, x = x)
data <- data[data$y > 0, ]

additiveModel <- vgam(y ~ s(x, df = 3), data = data, family = pospoisson())

summary(estimatePopsize(additiveModel))
```

We see that `1000` is well with confidence intervals and that estimates for `x` are approximately correct:

```{r plotVGAM}
plotvgam(additiveModel, data)
```
with the actual curve being:
```{r curve, echo=FALSE}
curve(cos, from = min(x), to = max(x))
```

We also allow bootstrap methods:
```{r VGAMboot}
x <- rnorm(n = 1000)
y <- rpois(n = 1000, lambda = exp(-1 + x))
data <- data.frame(y = y, x = x)
data <- data[data$y > 0, ]
m1 <- vglm(y ~ x, data = data, family = pospoisson())
singleRm1 <- estimatePopsize(m1, popVar = "bootstrap")
summary(singleRm1)
```

The `plots` method that is available for native `singleRcapture` object are also 
(being) developed for `singleRcaptureExtra` objects (`singleRforeign` class)

```{r bootHist}
plot(singleRm1, plotType = "bootHist", ylim = c(0, 220))
```

Diagnostics from `singleRcapture` are also available:

```{r}
summary(marginalFreqVglm(singleRm1))
```

Utilising popular `countreg` package (compare with `singleRcapture`):
```{r countreg}
library(countreg)
model <- zerotrunc(
  formula = capture ~ gender + age + nation, 
  data = netherlandsimmigrant, 
  dist = "poisson"
)
print(summary(estimatePopsize(model)), 
      # Print summary of foreign object (works for all methods)
      summaryForeign = TRUE)

model <- estimatePopsize(
  formula = capture ~ gender + age + nation, 
  data = netherlandsimmigrant, 
  model = singleRcapture::ztpoisson
)
summary(model)
```



## Funding

Work on this package is supported by the the National Science Center, OPUS 20 grant no. 2020/39/B/HS4/00941.   
